Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-15 trunk/constantRate/ConstCompFuzzExt-reorg.tex
modified reusability definition

We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}

\begin{definition}[Insider Reusable Fuzzy Extractors]
\label{def:reusable fuzz}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.  Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.  We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
\begin{align*}
\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
\end{align*}
\end{definition}

\subsection{Coding Theory}
\label{sec:coding theory}
We will consider slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
\end{definition}

\textbf{Notes:}
Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.  See Constructions~\ref{cons:first construction} and~\ref{cons:sampling} for the translation between the error classes.

@@

\begin{theorem}
\label{thm:reusability}
Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.  Then \consref{cons:sampling} is $q$-reusable.
\end{theorem}
\begin{proof}
The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.
\end{proof}

\subsection{Discussion of \consref{cons:sampling}}
\lnote{I need to check this}
We now show \consref{cons:sampling} supports partial block sources with $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.  We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.  However, we do achieve reusability for an arbitrary size alphabet, this has not been achieved in previous works.

\section{Allowing Correlated Symbols}
In the previous two sections, we presented constructions that supported $\Huse\le 0$ for restricted classes of distributions.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting $\Huse \le 0$ and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

>>>>

We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
%We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
%\begin{definition}[Insider Reusable Fuzzy Extractors]
%\label{def:reusable fuzz}
%Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.  Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.  We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
%\begin{align*}
%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
%\end{align*}
%\end{definition}
Our definition is a modified form of the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We first present the modified definition and then discuss the differences between our definition and that of Boyen.
\begin{definition}[Outsider Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game~(for each $W_1\in \mathcal{W}$ and for all $i=1,..., q$):
\begin{itemize}
\item[Sampling] The challenger samples $w_1\leftarrow W_1$.
\item[Perturbation] For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.  The challenger sets $w_{i+1} = \delta_i(w_1)$.
\item[Distinguishing] The advantage of $D$ is
\[
\epsilon_{sec}\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1] - \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\]
where $u$ is a uniformly random string.
\end{itemize}
Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  We say that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D$ of size at most $s_{sec}$ they win the game with advantage at most $\epsilon_{sec}$.
\end{definition}

\paragraph{Adapting the definition of Boyen to the computational setting:} 
The definition of Boyen considers a single adversary.  We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.  The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.  However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to require the entire adversary to be computationally bounded.  Our construction satisfies this alternative adaption as well.}

Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.  This was not allowed in the definition of Boyen as it would make security impossible.

Finally, we allow the distinguishing adversary to see other keys.  This is strictly stronger than the definition of Boyen.  However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.  This is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.  Our reusable construction~(\consref{cons:sampling}) is not insider secure.

The definition is parameterized by $f_2,..., f_q$.  This adversary implicitly defines distributions $W_2,..., W_q$~(which depend on $W_1$ and the public values $P_1,... P_i$).  Security seems hopeless if fuzzy extractor is not secure on each of these distributions on their own.  This is the only requirement we make on these functions.  We call these types of functions admissible:

\begin{definition}
Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  In the reusability game above, we say a set of functions $f_2,..., f_q$ are \emph{admissible} if for all $W_1\in \mathcal{W}$ for all $w_1\in W_1$ and $\forall p_1,..., p_q$ that are the public outputs of $\gen$ the implicit distribution $W_{i,w_1,p_1,..., p_{i-1}} = f_i(w_1,p_1,..., p_{i-1})$ is a member of $\mathcal{W}$.   
\end{definition}

@@

\begin{theorem}
\label{thm:reusability}
Let $q = \poly(n)$, and let all the variables be as in \thref{thm:sampling}, except that $\mathcal{O}$ be an $\ell\times q$-composable VGB obfuscator for digital lockers~(with $\kappa$ bit outputs) with auxiliary inputs.  For any admissible $f_2,..., f_q$, for all $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable fuzzy extractor.
\end{theorem}
\begin{proof}
The only modification to the outline presented in \secref{ssec:sec cons sampling} is in \lemref{lem:samp unguess} with the other keys $R_1,..., R_{i-1}, R_{i+1}, ..., R_q$ treated as additional auxiliary input to the adversary/simulator.  The simulator in the definition of composable obfuscation is required to function for arbitrary circuits in the family even if the choice of these circuits depends on the previous obfuscations.
\bnote{almost certainly need to say more here.  expand}
\end{proof}

\subsection{When is $\Huse\le 0$?}
\consref{cons:sampling} supports partial block sources with $\Huse\le 0$.  The required entropy of partial block source is $\alpha (\gamma-\beta ) = \Theta(\gamma)$.  We are able to correct $o(\gamma)$ errors.
This yields:
\[
\Huse = \Hoo(W) -\log |B_t| < \Theta(\gamma)- t \log |\mathcal{Z}|= \Theta(\gamma) - o(\gamma) \log |\mathcal{Z}|
\]
That is, there exists a super-constant alphabet size for which \consref{cons:sampling} is secure with $\Huse\le 0$.  We note that \consref{cons:sampling} works for an arbitrary size alphabet; however, for a constant size alphabet, $\Huse>0$.  However, we do achieve reusability for an arbitrary size alphabet, this has not been achieved in previous works.

\section{Allowing Correlated Symbols}
In the previous two sections, we presented constructions that supported $\Huse\le 0$ for restricted classes of distributions.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting $\Huse \le 0$ and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.  Before presenting the construction we provide some definitions from error correcting codes.
We use slightly nonstandard error-correct codes over $\{0,1\}^\ell$, which correct up to $t$ bit flips from $0$ to $1$ but no bit flips from $1$ to $0$ (this is the Hamming analog of the $Z$-channel~\cite{tallini2002capacity}).\footnote{Any code that corrects $t$ Hamming errors also corrects $t$ $0\rightarrow 1$ errors, but more efficient codes  exist for this type of error~\cite{tallini2002capacity}.
Codes with $2^{\Theta(\ell)}$ codewords and $t = \Theta(\ell)$ over the binary alphabet exist for Hamming errors and suffice for our purposes~(first constructed by Justensen~\cite{justesen1972class}).  These codes also yield a constant error tolerance for $0\rightarrow 1$ bit flips.
The class of errors we support in our source~($t$ Hamming errors over a large alphabet) and the class of errors for which we need codes~($t$ $0\rightarrow 1$ errors) are different.  
}
\begin{definition}
\label{def:hamming z channel}
For a point $c\in \zo^\ell$ define $\neigh_t(c) $ as the set of all points where at most $t$ bits $c_i$ are changed from $0$ to $1$.
\end{definition}
